Relative parabolic factorizations of Chevalley groups

### 2015-05-20 bass-kolster.tex
Fixed minor error

\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$:}
Notice that column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_\ell, I)$.

We can find $f_1, f_2,\ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
Set $\xi = v''_1-v''_{-1}-1 \in I$, $h_2 = \prod_{i=1}^{-2} t_{-1,i}(\xi \cdot f_i) \in \U(\Sigma_\ell, I)$.
Now it is clear that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.

>>>>

\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$:}
Notice that column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_1, I)$.

We can find $f_1, f_2,\ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
%TODO: Determine exact sign
Set $\xi = v''_1-v''_{-1}-1 \in I$, $h_2 = t_{-1,1}(\xi f_1 \pm \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}) \cdot \prod_{i=2}^{-2} t_{-1,i}(\xi f_i) \in \U(\Sigma_1, I)$.
Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.
